---
title: "Example of using main features of the anrep class API"
author: "Andrey Tovchigrechko"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example of using main features of the anrep class API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette demonstrates how you would use methods of the `anrep` class in order to 
control the final structure of your report.

```{r}
library(anrepr)
```

An example source file is included with the package, and can be located with this command:
```{r cache=FALSE}
example_code_file <- system.file("examples", "example_sections.R", package = "anrepr",mustWork = TRUE)
```

Below is the code listing of that example. The code uses the anrep class API calls to create a report
with multiple nested sections and subreports and to insert a few plots and tables.
Look at the inline comments for the annotation of major steps.
```{r cache=FALSE, echo=FALSE}
knitr::read_chunk(example_code_file)
```
```{r example_sections_report_functions, cache=FALSE, results="hide", warning = FALSE, message = FALSE, comment=NA}
```

And then we run the report generation pipeline that we setup above. In this vignette code,
we told it not to export the generated Markdown code into HTML, in order to avoid
dependency on the external Pandoc executable.
```{r cache=FALSE, results="hide", warning = FALSE, message = FALSE}
make_example_sections_report("example_sections_report",export=F)
```

During actual use on your own system where you installed Pandoc, you would instead call:
```{r eval=FALSE, cache=FALSE, results="hide", warning = FALSE, message = FALSE}
make_example_sections_report("example_sections_report")
```

Look at the [resulting HTML report](example_sections_report/report-1.html) which is also included 
with the package.

